The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2020-01-31 Paper/jaccardbaetica.tex
add new changes

\section{Material and Methods}

@@

We studied a dataset of 3798 stamps collected from different Dressel 20 amphora workshops in Baetica province. The stamp database was compiled by CEIPAC database \citep{remesal_centro_2015} (see CEIPAC database here \url{http://romanopendata.eu}). However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps comprised of 130 different stamps from 81 workshops. The frequency of stamps per workshop can be seen in Fig. \ref{stamps}. Most stamps are distributed in only one workshop whereas few workshops concentrate a high frequency of different amphoric stamps.

@@

@@

%\xavi{gráfico molón, y útil; haría los puntos y letras de los ejes más gordos solo}

%\xavi{entiendo que són códigos, no sellos? Estaría bien también mostrar cuántos sellos se encuentran por yacimiento.}
%explicar por qué: mayor intensifación en las excavaciones quizás en sevilla

%explicar las razones del conventus no?
%aquí hablar de sellos?

%los sellos fueron marcados a partir del siglo II d.C (la economía oleícola bética Remesal) hablar de stams más concreto

\subsection{Consumption centres}

@@

\subsection{Britannia}

\subsubsection{Jaccard distance}

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

(EXTENDER)

\subsubsection{Morisita-Horn index}

\xavi{este titulín es mejorable :-D}

>>>>

\section{Material and methods}

@@

\subsubsection{Material}

We studied a dataset of 3798 stamps collected from different Dressel 20 amphora workshops in Baetica province. The stamp database was compiled by CEIPAC database \citep{remesal_centro_2015} (see CEIPAC database here \url{http://romanopendata.eu}). However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps comprised of 130 different stamps from 81 workshops.

@@

\subsubsection{Exploratory Analysis}

We calculated the frequency of distribution in amphora stamps with the aims to carry out a exploratory analysis (EDA) to know the distribution and the number of stamps per each centre.

The frequency of stamps per workshop can be seen in Fig. \ref{stamps}. Most stamps are distributed in only one workshop whereas few workshops concentrate a high frequency of different amphoric stamps. The type of distribution is also frequent in Roman economy where we observed a self-organized complex system patterns typical of a free market \citep{coto-sarmiento_maria_bayesian_????}.

@@

\subsection{Consumption centres: Britannia and Germania}

@@

\subsubsection{Britannia}

\subsubsection{Material}

We analysed a dataset of 2219 stamps from different centres in Britannia. 
%CITAR (Callender, 1965; Carreras Monfort y Funari,1998; Ayllón-Martı́ et al., 2018). 
The stamp database was also compiled by CEIPAC database. The database contained anomalies that were eliminated using the same criteria cited above. We finally selected the centres with more or equal than 5 stamps. As a result, we studied a total of 1765 stamps comprised of 968 different stamps from 46 centres.
The centres can be seen in Fig.\ref{britannia}.

\begin{figure}[htp]
	\centering
\includegraphics[width=\linewidth]{figs/britmap.pdf}
\caption{Distribution of centres in Britannia}
\label{britannia}
\end{figure}

%\subsubsection{Jaccard distance}
%The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

\subsection{Measuring the dissimilarity in stamps}

%\xavi{este titulín es mejorable :-D}
